Neural dialogue act recognition with transformer pre-training

### 2019-04-06 abstract.tex
shorten the references, small comment
typo

However, given that BERT is pre-trained on book and encyclopedia data, 
there is no guarantee it will improve performance on dialogue-specific tasks.
Adding to that uncertainty, we note that word2vec is not consistently beneficial for DAR \citep{cerisaraEffectsUsingWord2vec2017}.
To assess BERT's potential for dialogue applications, we propose a series of DAR experiments 
with various utterance encoders, including BERT.
Utterance representations are then fed to a simple RNN to predict sequences of dialogue acts.
In particular, we are interested in whether BERT can be fine-tuned to adequately represent
dialogue-specific features such as discourse markers, disfluency, and laughter.

@@

  Pre-trained models benefit from learning on large amounts of online data, however it might be the case that for DAR, additional information only present in natural dialogue data will be useful. In SWDA disfluencies are annotated and for the datasets where no annotation for disfluencies is available, they can be predicted from recognized speech \citep{hough2017joint,shalyminov2018multi}. We evaluate the impact of disfluencies and non-verbal signals, such as laughters on the performance of our models and suggests the ways to include information about disfluencies in pre-trained models.

>>>>

However, given that BERT is pre-trained on book and encyclopedia data, 
there is no guarantee it will improve performance on dialogue-specific tasks.
Adding to that uncertainty, we note that word2vec is not consistently beneficial for DAR \citep{cerisaraEffectsUsingWord2vec2017}.
To assess BERT's potential for dialogue applications, we propose a series of DAR experiments 
with various utterance encoders, including BERT.
Utterance representations are then fed to a simple RNN to predict sequences of dialogue acts.
In particular, we are interested in whether BERT can be fine-tuned to adequately represent
dialogue-specific features such as discourse markers, disfluency, and laughter. \textbf{Vlad: disfluencies? maybe non-verbal vocalisations (such as laughter) instead of laughter?}

@@

  Pre-trained models benefit from learning on large amounts of online data, however it might be the case that for DAR, additional information only present in natural dialogue data will be useful. In SWDA disfluencies are annotated and for the datasets where no annotation for disfluencies is available, they can be predicted from recognized speech \citep{hough2017joint,shalyminov2018multi}. We evaluate the impact of disfluencies and non-verbal signals, such as laughters on the performance of our models and suggest the ways to include information about disfluencies in pre-trained models.
